---
title: "CRGE Historical Database - English"
---

```{r}
#| label: setup
#| include: false
library(dplyr)
library(glue)
library(knitr)

# Load the full dataset
df <- read.csv("../data.csv", stringsAsFactors = FALSE)
```

# CRGE Historical Database

Welcome to the English version of the **CRGE Historical Database**, a comprehensive resource documenting Christian missionary history and religious agency in East Asia.

<div style="text-align: right; margin-bottom: 1rem;">
<a href="../zh/index.html" style="text-decoration: none; color: #dc3545; font-weight: bold;">切换到中文 →</a>
</div>

## About This Database

This digital archive contains extensive documentation of Christian missionary activities, religious movements, and cultural interactions across East Asian regions including China, Korea, Japan, Taiwan, Hong Kong, and Manchuria. The content spans from the late 19th century through the modern era, offering insights into the complex relationships between Christianity and local societies.

## Database Overview

```{r}
#| label: database_stats
#| results: asis
#| echo: false

# Calculate basic statistics
total_entries <- nrow(df)
total_areas <- length(unique(df$area[!is.na(df$area) & df$area != ""]))
total_periods <- length(unique(df$period[!is.na(df$period) & df$period != ""]))
total_topics <- length(unique(df$topic[!is.na(df$topic) & df$topic != ""]))

# Count entries with English content
entries_with_content <- df %>%
  filter(!is.na(text_en), nzchar(text_en)) %>%
  nrow()

cat(glue("- **Total Database Entries:** {format(total_entries, big.mark = ',')}\n"))
cat(glue("- **Geographic Areas:** {total_areas}\n"))
cat(glue("- **Time Periods:** {total_periods}\n"))
cat(glue("- **Topics Covered:** {total_topics}\n"))
cat(glue("- **Entries with English Content:** {format(entries_with_content, big.mark = ',')}\n\n"))
```

---

*Center on Religion and the Global East*
